Distributions

### 2022-01-06 Ch2_distributions/Ch2_Figures.Rmd
Figure x. ready.

figx.theme <- theme_bw() +
  theme(legend.position = "none")

cp.best %>% 
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog)) +
  geom_point(alpha = aval) +
  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
  figx.theme -> cp.ln

cp.best %>%
  filter(., dist == "weibull") %>% 
  ggplot(., aes(x = scale, y = shape)) +
  geom_point(alpha = aval) +
  lims(x = c(5, 80), y = c(0, 2.1)) +
  figx.theme -> cp.wei

@@

pp.best %>% 
  filter(., dist == "gamma") %>% 
  ggplot(., aes(x = rate, y = shape, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(0, 0.23), y = c(0.4, 2.3)) +
  figx.theme -> pp.gam

pp.best %>%
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
  figx.theme -> pp.ln

pp.best %>%
  filter(., dist == "weibull") %>% 
  ggplot(., aes(x = scale, y = shape, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(5, 80), y = c(0, 2.1)) +
  figx.theme -> pp.wei

@@

np.best %>% 
  filter(., dist == "gamma") %>% 
  ggplot(., aes(x = rate, y = shape, color = group, shape = shapeid)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(0, 0.23), y = c(0.4, 2.3)) +
  figx.theme -> np.gam

np.best %>% 
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog, color = group, shape = shapeid)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
  figx.theme -> np.ln

np.best %>%
  filter(., dist == "weibull") %>% 
  ggplot(., aes(x = scale, y = shape, color = group, shape = shapeid)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(5, 80), y = c(0, 2.1)) +
  figx.theme -> np.wei

>>>>

figx.theme <- theme_bw() +
  theme(legend.position = "none",
        axis.title = element_text(size = 8))

cp.best %>% 
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog)) +
  geom_point(alpha = aval) +
  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
  labs(subtitle = "CP - lnorm") +
  figx.theme -> cp.ln

cp.best %>%
  filter(., dist == "weibull") %>% 
  ggplot(., aes(x = scale, y = shape)) +
  geom_point(alpha = aval) +
  lims(x = c(5, 80), y = c(0, 2.1)) +
  labs(subtitle = "CP - weibull") +
  figx.theme -> cp.wei

@@

pp.best %>% 
  filter(., dist == "gamma") %>% 
  ggplot(., aes(x = rate, y = shape, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(0, 0.23), y = c(0.4, 2.3)) +
  labs(subtitle = "PP - gamma") +
  figx.theme -> pp.gam

pp.best %>%
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
  labs(subtitle = "PP - lnorm") +
  figx.theme -> pp.ln

pp.best %>%
  filter(., dist == "weibull") %>% 
  ggplot(., aes(x = scale, y = shape, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(5, 80), y = c(0, 2.1)) +
  labs(subtitle = "PP - weibull") +
  figx.theme -> pp.wei

@@

np.best %>% 
  filter(., dist == "gamma") %>% 
  ggplot(., aes(x = rate, y = shape, color = group, shape = shapeid)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(0, 0.23), y = c(0.4, 2.3)) +
  labs(subtitle = "NP - gamma") +
  figx.theme -> np.gam

np.best %>% 
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog, color = group, shape = shapeid)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
  labs(subtitle = "NP - lnorm") +
  figx.theme -> np.ln

np.best %>%
  filter(., dist == "weibull") %>% 
  ggplot(., aes(x = scale, y = shape, color = group, shape = shapeid)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(5, 80), y = c(0, 2.1)) +
  labs(subtitle = "NP - weibull") +
  figx.theme -> np.wei
